---
title: "Pacote SPTrans"
author: "Julio Trecenti"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Pacote SPTrans}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` setion of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))

_____

```{r, warning=FALSE, message=FALSE}
# Bibliotecas usadas
# library(dplyr)
# library(ggplot2)
# load('shapes.RData')
```

```{r, warning=FALSE, message=FALSE}
# p <- shapes %>%
#   ggplot(aes(x=shape_pt_lon, y=shape_pt_lat, colour=shape_id, group=shape_id)) +
#   geom_path(alpha=.1) +
#   coord_equal() +
#   theme_bw()
# print(p)
```

```{r, warning=FALSE, message=FALSE}
# library(ggmap)
# map <- get_map(location = 'São Paulo, SP, Brazil', zoom = 10, maptype='roadmap')
# p <- map %>% ggmap +
#   geom_path(aes(x=shape_pt_lon, y=shape_pt_lat, group=shape_id), colour='red', data=shapes, alpha=.1)
# print(p)
```




